---
title: "thesis_data_analysis"
author: "Luis Luarte"
date: '2022-06-03'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# load libs

```{r}
pacman::p_load(
  tidyverse,
  ggplot2,
  rstudioapi,
  devtools,
  lme4,
  lmerTest,
  ggpubr,
  ggthemes,
  sjPlot
)

# source lickometer library
devtools::source_url("https://github.com/lab-cpl/lickometer-library/blob/main/src/lickometer_functions_compilate.R?raw=TRUE")

```

# load data sets

This data sets correspond to experiments where FED food delivery was random, and
motivation was tested using a progressive ratio in lickometer

```{r}
# set working directory where this file is located
cur_dir <- dirname(getSourceEditorContext()$path)
setwd(cur_dir)

# lickometer data for both pool with low and high uncertainty
lickometer_uncertainty <- readRDS("../data/raw/lickometer_data.rds")

# fed data for both pool with low and high uncertainty
fed_high_uncertainty <- readRDS("../data/raw/high_uncertainty.rds")
fed_low_uncertainty <- readRDS("../data/raw/low_uncertainty.rds")

# merge both fed data sets
fed_uncertainty <- bind_rows(
  fed_high_uncertainty,
  fed_low_uncertainty
)

# weight data
weight_uncertainty <- readRDS("../data/raw/weights.rds")
```

# data processing

## intake

```{r}
# this data proc is to plot intake

# first get intake over days per mouse
intake_over_days <- fed_uncertainty %>% 
  # add light/dark periods
  mutate(
    light_dark = case_when(
      hour_of_day >= 11 & hour_of_day <= 23 ~ "dark",
      TRUE ~ "light"
    )
  ) %>% 
  group_by(
    animal,
    ymd,
    experiment_id,
    protocol
  ) %>% 
  summarise(
    pellets_per_day = max(pellets)
  ) %>% 
  ungroup() %>% 
  group_by(
    animal
  ) %>% 
  mutate(
    pellets_cumm = cumsum(pellets_per_day)
  ) %>% 
  filter(
    protocol %in% c("experimental", "control")
  ) %>% 
  ungroup() %>% 
  group_by(
    animal
  ) %>% 
  mutate(
    session = as.numeric(as.factor(ymd))
  ) %>% 
  # max number of sessions for all pools
  # 246 was euthanized
  filter(session <= 35, animal != 246) %>% 
  # group both controls together
  mutate(
    group = case_when(
      protocol == "control" ~ "control",
      protocol == "experimental" &
        experiment_id == "high_uncertainty_fed" ~ "experimental_high_unc",
      protocol == "experimental" &
        experiment_id == "low_uncertainty_fed" ~ "experimental_low_unc"
    )
  )

# intake model
intake_mdl <- lmer(
  data = intake_over_days %>% filter(session > 7),
  pellets_per_day ~ group * session + (1 | animal)
)
summary(intake_mdl)
confint(intake_mdl)

# cummulative intake over days summarized to present data based on
# experimental protocol
intake_over_days_group <- intake_over_days %>% 
  group_by(
    group,
    session
  ) %>% 
  summarise(
    pellets_cumm_group = mean(pellets_cumm),
    err = sd(pellets_cumm) / sqrt(n())
  )

# mean intake per group
intake_means <- intake_over_days %>% 
  group_by(
    group,
    session,
    animal
  ) %>% 
  summarise(
    pellets_mean = mean(pellets_per_day)
  ) %>% 
  ungroup() %>% 
  group_by(
    group,
    session
  ) %>% 
  summarise(
    pellets_mean_session = mean(pellets_mean)
  ) %>% 
  ungroup() %>% 
  group_by(
    group
  ) %>% 
  summarise(
    pellets_mean_group = mean(pellets_mean_session),
    err = sd(pellets_mean_session) / sqrt(n())
  )

# intake with light dark periods
intake_over_days_circ <- fed_uncertainty %>% 
  # add light/dark periods
  mutate(
    light_dark = case_when(
      hour_of_day >= 11 & hour_of_day <= 23 ~ "dark",
      TRUE ~ "light"
    )
  ) %>% 
  group_by(
    animal,
    ymd,
    experiment_id,
    protocol,
    light_dark
  ) %>% 
  summarise(
    pellets_per_day = max(pellets)
  ) %>% 
  ungroup() %>% 
  group_by(
    animal
  ) %>% 
  mutate(
    pellets_cumm = cumsum(pellets_per_day)
  ) %>% 
  filter(
    protocol %in% c("experimental", "control")
  ) %>% 
  ungroup() %>% 
  group_by(
    animal
  ) %>% 
  mutate(
    session = as.numeric(as.factor(ymd))
  ) %>% 
  # max number of sessions for all pools
  # 246 was euthanize
  filter(session <= 35, animal != 246) %>% 
  # group both controls together
  mutate(
    group = case_when(
      protocol == "control" ~ "control",
      protocol == "experimental" &
        experiment_id == "high_uncertainty_fed" ~ "experimental_high_unc",
      protocol == "experimental" &
        experiment_id == "low_uncertainty_fed" ~ "experimental_low_unc"
    )
  )

# inter-pellet recovery time
inter_pellet_recovery <- fed_uncertainty %>% 
  mutate(
    session = as.numeric(as.factor(ymd))
  ) %>% 
  group_by(animal) %>% 
  mutate(
    inter_pellet_recovery = (hms - lag(hms)) - delay
  ) %>% 
  # na here are the first pellet which is set while leaving the FED inside the cage
  drop_na() %>% 
  ungroup() %>% 
  # remove double pellets > 3% chance
  # double pellets generate events that are faster than delay
  filter(
    inter_pellet_recovery > 0
  )

# now we want inter-pellet recovery estimate by animal and session
inter_pellet_recovery_ind <- inter_pellet_recovery %>% 
  group_by(
    animal,
    session,
    protocol,
    experiment_id
  ) %>% 
  summarise(
    mean_recovery = mean(inter_pellet_recovery)
  ) %>% 
  # now session is collapsed to obtain an estimate per animal
  ungroup() %>% 
  group_by(
    animal,
    protocol,
    experiment_id
  ) %>% 
  summarise(
    mean_recovery_id = mean(mean_recovery)
  )
# inter-pellets recovery by group
inter_pellet_recovery_group <- inter_pellet_recovery_ind %>% 
  ungroup() %>% 
  group_by(
    protocol,
    experiment_id
  ) %>% 
  summarise(
    mean_recovery_group = mean(mean_recovery_id),
    err = sd(mean_recovery_id) / sqrt(n())
  )
  
```

## weight 
```{r}
weight_uncertainty <- readRDS("../data/raw/weights.rds")
# create control and experimental groups
weight_uncertainty <- weight_uncertainty %>% 
  mutate(
    group = case_when(
      animal %in% c(320, 323, 325, 326) ~ "experimental_high_unc",
      animal %in% c(234, 235, 236, 245, 265) ~ "experimental_low_unc",
      TRUE ~ "control"
    )
  )

# add groups
# first we get them from fed_uncerainty data
groups <- fed_uncertainty %>% 
  select(
    animal,
    protocol,
    ymd
  ) %>% 
  distinct(., ymd, .keep_all = TRUE)
# add the group into weight data
weight_uncertainty <- weight_uncertainty %>% 
  left_join(groups, by = c("animal", "date" = "ymd")) %>% 
  filter(protocol %in% c("experimental", "control"))

weight_change <- weight_uncertainty %>% 
  group_by(
    animal
  ) %>% 
  mutate(
    dw = ((weight - weight[1]) / weight[1]) * 100
  ) %>% 
  do(tail(., n=3))

w_mdl <- lm(
  data = weight_change,
  dw ~ group
)
summary(w_mdl)

# calculate percent difference between days
weight_uncertainty <- weight_uncertainty %>% 
  group_by(
    animal,
    experiment_id
  ) %>% 
  mutate(
    init_weight = weight[1],
    delta_bw = ((weight - init_weight) / ((weight + init_weight) / 2)) * 100,
    cumm_delta_bw = cumsum(delta_bw),
    session = as.numeric(as.factor(date))
  ) %>% 
  # right number of weight sessions
  filter(session <= 16)

# get means per group per session
weight_uncertainty_group <- weight_uncertainty %>% 
  group_by(
    session,
    group
  ) %>% 
  summarise(
    weight_mean = mean(delta_bw),
    err = sd(weight) / sqrt(n())
  )

# get mean per group
weight_uncertainty_group_ <- weight_uncertainty_group %>% 
  group_by(
    group
  ) %>% 
  summarise(
    weight_mean_ = mean(weight_mean),
    err_ = sd(weight_mean) / sqrt(n())
  )

# get number of pellets / delta bw
# merge intake over days with weight data
intake_weight <- intake_over_days %>% 
  left_join(weight_uncertainty %>% 
              select(animal, weight, date), by = c("animal", "ymd" = "date"))
# impute missing data with a rolling average
intake_weight_imputation <- intake_weight %>% 
  group_by(
    animal
  ) %>% 
  mutate(
    rolling_weight = zoo::rollapply(weight, 5, mean, fill = 0, na.rm = TRUE)
  ) %>% 
  ungroup() %>% 
  filter(rolling_weight != 0) %>% 
  group_by(
    animal,
    session
  ) %>% 
  mutate(
    pellets_per_gr = pellets_per_day / rolling_weight
  ) 
# calculate means per session
intake_weight_session <- intake_weight_imputation %>% 
  group_by(
    session,
    group
  ) %>% 
  summarise(
    pellets_per_gr_mean = mean(pellets_per_gr),
    err = sd(pellets_per_gr) / sqrt(n())
  )
# calculate means per group
intake_weight_group <- intake_weight_session %>% 
  group_by(
    group
  ) %>% 
  summarise(
    pellets_per_gr_mean_group = mean(pellets_per_gr_mean),
    err = sd(pellets_per_gr_mean) / sqrt(n())
  )

# same idea but with light dark periods
# get number of pellets / delta bw
# merge intake over days with weight data
intake_weight_circ <- intake_over_days_circ %>% 
  left_join(weight_uncertainty %>% 
              select(animal, weight, date), by = c("animal", "ymd" = "date"))
# impute missing data with a rolling average, add from the previously calculated
intake_weight_imputation_circ <- intake_weight_circ %>% 
  select(-session) %>% 
  left_join(intake_weight_imputation %>% 
              select(
                animal,
                ymd,
                rolling_weight
              ), by = c("animal", "ymd")) %>% 
  ungroup() %>% 
  filter(rolling_weight != 0) %>% 
  group_by(
    animal,
    session,
    light_dark
  ) %>% 
  mutate(
    pellets_per_gr = pellets_per_day / rolling_weight
  ) 

# calculate means per session
intake_weight_session_circ <- intake_weight_imputation_circ %>% 
  group_by(
    session,
    group,
    light_dark
  ) %>% 
  summarise(
    pellets_per_gr_mean = mean(pellets_per_gr),
    err = sd(pellets_per_gr) / sqrt(n())
  )
# calculate means per group
intake_weight_group_circ <- intake_weight_session_circ %>% 
  group_by(
    group,
    light_dark
  ) %>% 
  summarise(
    pellets_per_gr_mean_group = mean(pellets_per_gr_mean),
    err = sd(pellets_per_gr_mean) / sqrt(n())
  )
```
## lickometer

### preference
```{r}
# add relevant labels: experimental group and protocol

labels <- weight_uncertainty %>% 
  select(animal, group, protocol, experiment_id) %>% 
  distinct(., animal, .keep_all = TRUE) %>% 
  rename(ID = animal)


lickometer_data <- lickometer_uncertainty %>% 
  left_join(
    labels,
    by = c("ID")
  ) %>% 
  # add session instead of dates
  group_by(
    group,
    task_type
  ) %>% 
  mutate(
    session = as.numeric(as.factor(fecha))
  ) %>% 
  ungroup()

# preference for sucrose
spout_pref <- lickometer_data %>% 
  group_by(
    ID,
    group,
    protocol,
    tipo_recompensa,
    session,
    task_type,
    fecha,
    experiment_id
  ) %>% 
  summarise(
    n_licks = n(),
    n_events = max(evento)
  )

# preference for sucrose in FR
spout_pref_fr <- spout_pref %>% 
  filter(task_type == "fr") %>% 
  group_by(
    group,
    protocol,
    tipo_recompensa,
    session,
    fecha
  ) %>% 
  summarise(
    mean_licks = mean(n_licks)
  ) %>% 
  ungroup() %>% 
  group_by(
    group,
    protocol,
    fecha
  ) %>% 
  mutate(
    total_licks = sum(mean_licks),
    relative_licks = (mean_licks / total_licks) * 100
  ) %>% 
  ungroup() %>% 
  group_by(
    group,
    protocol,
    tipo_recompensa
  ) %>% 
  summarise(
    mean_licks_group = mean(relative_licks), 
    err = sd(relative_licks) / sqrt(n())
  )
```

### PR structure
```{r}

pr_data <- lickometer_data %>% 
  group_by(
    ID,
    group,
    protocol,
    tipo_recompensa,
    session,
    task_type,
    fecha,
    experiment_id
  ) %>% 
  summarise(
    n_licks = n(),
    n_events = max(evento)
  )

pr_sessions <- pr_data %>% 
  filter(task_type == "pr") %>% 
  group_by(
    group,
    protocol,
    experiment_id
  ) %>% 
  mutate(
    session = as.numeric(as.factor(fecha)),
    valid_session = if_else(protocol == "control" & session > 7, 0, 1)
  ) %>% 
  # consider only sucrose licks and events
  filter(valid_session == 1, tipo_recompensa == "sacarosa") %>% 
  select(-valid_session) %>% 
  # re compute standarized mean after merging both controls group together
  mutate(
    experiment_id = if_else(protocol == "control", "control", experiment_id)
  ) %>% 
  # z-score licks and events
  group_by(
    ID
  ) %>% 
  mutate(
    n_licks_z = scale(n_licks),
    n_events_z = scale(n_events)
  ) %>% 
  ungroup() %>% 
  # obtain group estimates
  group_by(
    protocol,
    group,
    experiment_id,
    session
  ) %>% 
  summarise(
    mean_licks = mean(n_licks),
    mean_events = mean(n_events),
    err_licks = sd(n_licks) / sqrt(n()),
    err_events = sd(n_events) / sqrt(n())
  )

pr_sessions_mdl <- pr_data %>% 
  filter(task_type == "pr") %>% 
  group_by(
    group,
    protocol,
    experiment_id
  ) %>% 
  mutate(
    session = as.numeric(as.factor(fecha)),
    valid_session = if_else(protocol == "control" & session > 7, 0, 1)
  ) %>% 
  # consider only sucrose licks and events
  filter(valid_session == 1, tipo_recompensa == "sacarosa") %>% 
  select(-valid_session) %>% 
  # re compute standarized mean after merging both controls group together
  mutate(
    experiment_id = if_else(protocol == "control", "control", experiment_id)
  ) %>% 
  # z-score licks and events
  group_by(
    ID
  ) %>% 
  mutate(
    n_licks_z = scale(n_licks),
    n_events_z = scale(n_events)
  ) %>% 
  ungroup()
```
## lickometer plots and stats

### licks over session stats
```{r}
licks_model <- lmer(
  data = pr_sessions_mdl,
  n_licks ~ group * session + (1 | ID)
)
summary(licks_model)
confint(licks_model)

licks_model_fct <- lmer(
  data = pr_sessions_mdl,
  n_licks ~ group * as.factor(session) + (1 | ID)
)
summary(licks_model_fct)
emmeans::emmeans(licks_model_fct, pairwise~group|session) %>% 
  summary(adjust = "none")
```

### microstructure
```{r}
pr_micro <- lickometer_data %>% 
  filter(task_type == "pr")

pr_micro <- pr_micro %>% 
  group_by(
    ID,
    group,
    protocol,
    tipo_recompensa,
    session,
    task_type,
    fecha,
    experiment_id
  ) %>% 
  mutate(interval = tiempo - lag(tiempo, default = NA))

ili <- burst_analysis(pr_micro, 500)

# number of clusters
clusters <- ili %>% 
  ungroup() %>% 
  filter(values == "in_cluster") %>% 
  group_by(
    ID,
    group,
    tipo_recompensa,
    n_sesion
  ) %>% 
  summarise(
    n_cluster = n()
  ) %>% 
  mutate(n_sesion = as.numeric(n_sesion)) %>% 
  filter(tipo_recompensa == "sacarosa")

clusters_m <- clusters %>% 
  group_by(
    group,
    n_sesion
  ) %>% 
  summarise(
    m = mean(n_cluster),
    s = sd(n_cluster) / sqrt(n())
  )

clusters_m %>% 
  ggplot(aes(
    n_sesion,
    m,
    ymin = m - s,
    ymax = m + s,
    fill = group
  )) +
  geom_col(position = "dodge") +
  geom_errorbar(width = 0.3, position = position_dodge(0.9)) +
  scale_fill_discrete(labels=c('Control', 'High uncertainty', 'Low uncertainty')) +
  theme_pubr() +
  ylab("Mean number of clusters") +
  xlab("Session number") +
  labs(fill='') +
  theme(legend.position = "right") +
  scale_x_continuous(breaks = 1:7)
ggsave("../images/figure4.png", width = 6, height = 4)


cluster_mdl <- lmer(
  data = clusters,
  n_cluster ~ group * n_sesion + (1 | ID)
)
summary(cluster_mdl)
confint(cluster_mdl)

cluster_mdl_fct <- lmer(
  data = clusters,
  n_cluster ~ group * as.factor(n_sesion) + (1 | ID)
)
emmeans::emmeans(cluster_mdl_fct, pairwise~group|n_sesion) %>% 
  summary(adjust = "tukey")

pm <- plot_model(cluster_mdl,show.p = TRUE, show.values = TRUE, p.shape = TRUE, rm.terms = c("groupexperimental_high_unc", "groupexperimental_low_unc", "n_sesion")) +
  ggtitle("") +
  theme(legend.position = "right") +
  ylab("Number of clusters") +
  xlab("Coefficients") +
  theme_pubr()
levels(pm$data$term) <- c("Low uncertainty : sessions", "High uncertainty : sessions")
pm
ggsave("../images/figure3.png", width = 6, height = 4)
```


### licks over sessions
```{r}
pr_sessions$group <- factor(pr_sessions$group, levels = c('control', 'experimental_low_unc', 'experimental_high_unc'))
pr_sessions %>% 
  ggplot(aes(
    session,
    mean_licks,
    fill = group
  )) +
  geom_col(position = "dodge") +
  geom_errorbar(aes(
    ymin = mean_licks - err_licks,
    ymax = mean_licks + err_licks
  ), width = 0.3, position = position_dodge(0.9)) +
  scale_fill_discrete(labels=c('Control', 'Low uncertainty', 'High uncertainty')) +
  theme_pubr() +
  ylab("Mean number of licks") +
  xlab("Session number") +
  labs(fill='') +
  theme(legend.position = "right") +
  scale_x_continuous(breaks = 1:7)
ggsave("../images/figure1.pdf", width = 6, height = 4)

plot_model(licks_model, type = "pred", terms = c("session", "group")) +
  ggtitle("") +
  theme_pubr() +
  theme(legend.position = "right") +
  scale_color_discrete(breaks = c('control', 'experimental_low_unc', 'experimental_high_unc'),
                       labels=c('Control', 'Low uncertainty', 'High uncertainty')) +
  labs(color = '') +
  ylab("Number of licks estimates") +
  xlab("Session number")
ggsave("../images/figure2.png", width = 6, height = 4)
```





# plots

## intake

### cummulative intake over days
```{r}
# cummulative intake over days
intake_over_days_group %>% 
  ggplot(aes(
    session,
    pellets_cumm_group,
    color = group,
    ymin = pellets_cumm_group - err,
    ymax = pellets_cumm_group + err
  )) +
  geom_point() +
  geom_line() +
  geom_errorbar(width = 0.3)
```
### mean intake per group
```{r}
intake_means %>% 
  ggplot(aes(
    group,
    pellets_mean_group,
    ymin = pellets_mean_group - err,
    ymax = pellets_mean_group + err,
    fill = group
  )) +
  geom_col() +
  geom_errorbar(width = 0.3) +
  theme_pubr() +
  ylab("Mean daily pellet intake") +
  xlab("") +
  labs(fill='') +
  theme(legend.position = "none") +
  scale_x_discrete(labels=c("Control","High uncertainty", "Low uncertainty"))
ggsave("../images/figure5.png", width = 6, height = 4)
```
### pellet intake per bw per session
```{r}
intake_weight_session %>% 
  ggplot(aes(
    session,
    pellets_per_gr_mean,
    color = group,
    ymin = pellets_per_gr_mean - err,
    ymax = pellets_per_gr_mean + err
  )) +
  geom_point() +
  geom_line() +
  geom_errorbar(width = 0.3)
```
### pellet intake per bw per group
```{r}
intake_weight_group %>% 
  ggplot(aes(
    group,
    pellets_per_gr_mean_group,
    ymin = pellets_per_gr_mean_group - err,
    ymax = pellets_per_gr_mean_group + err
  )) +
  geom_col() +
  geom_errorbar(width = 0.3)
```
### pellet intake per bw per group light/dark
```{r}
intake_weight_group_circ %>% 
  ggplot(aes(
    group,
    pellets_per_gr_mean_group,
    ymin = pellets_per_gr_mean_group - err,
    ymax = pellets_per_gr_mean_group + err,
    fill = light_dark
  )) +
  geom_col(position = "dodge") +
  geom_errorbar(width = 0.3, position = position_dodge(width = 0.9))
```

## weight

### delta body weight per session
```{r}
weight_uncertainty_group %>% 
  ggplot(aes(
    session,
    weight_mean,
    ymin = weight_mean - err,
    ymax = weight_mean + err,
    color = group
  )) +
  geom_point() +
  geom_line() + 
  geom_errorbar()
```
### delta body weight per group
```{r}
weight_uncertainty_group_ %>% 
  ggplot(aes(
    group,
    weight_mean_,
    ymin = weight_mean_ - err_,
    ymax = weight_mean_ + err_
  )) +
  geom_col() +
  geom_errorbar(width = 0.3)
```
## inter pellet recovery time
```{r}
inter_pellet_recovery_ind %>% 
  ggplot(aes(
    experiment_id,
    mean_recovery_id,
    group = protocol
  )) +
  geom_col(
    inherit.aes = FALSE,
    aes(
      experiment_id,
      mean_recovery_group,
      fill = protocol
    ),
    data = inter_pellet_recovery_group,
    position = "dodge"
  ) +
  geom_errorbar(
    inherit.aes = FALSE,
    aes(
      experiment_id,
      mean_recovery_group,
      fill = protocol,
      ymin = mean_recovery_group - err,
      ymax = mean_recovery_group + err
    ),
    data = inter_pellet_recovery_group,
    position = position_dodge(0.9),
    width = 0.3
  ) +
  geom_point(position = position_dodge(0.9), color = "gray70")
```

## lickometer plots

### preference for sucrose in fr
```{r}
spout_pref_fr %>% 
  ggplot(aes(
    group,
    mean_licks_group,
    ymin = mean_licks_group - err,
    ymax = mean_licks_group + err,
    fill = tipo_recompensa
  )) +
  geom_col(position = "dodge") +
  geom_errorbar(position = position_dodge(0.9), width = 0.3)
```
### progressive ratio licks over sessions
```{r}
pr_sessions %>% 
  ggplot(aes(
    session,
    mean_licks,
    ymin = mean_licks - err_licks,
    ymax = mean_licks + err_licks,
    color = experiment_id
  )) +
  geom_point() +
  geom_line() +
  geom_errorbar(width = 0.3) +
  facet_wrap(~group, scales = "free_x")
```
### progressive ratio events over sessions
```{r}
pr_sessions %>% 
  ggplot(aes(
    session,
    mean_events,
    ymin = mean_events - err_events,
    ymax = mean_events + err_events,
    color = experiment_id
  )) +
  geom_point() +
  geom_line() +
  geom_errorbar(width = 0.3) +
  facet_wrap(~group, scales = "free_x")
```
### progressive ratio licks in T.O over sessions
```{r}
peri_event_data_pr_bin %>% 
  ggplot(aes(
    peri_breaks,
    mean_n_licks,
    color = experiment_id,
    ymin = mean_n_licks - err,
    ymax = mean_n_licks + err
  )) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(fill = experiment_id)) +
  geom_vline(xintercept = 10.5)
```

### progressive ratio licks in T.O over session cumulative
```{r}
peri_event_data_pr_bin_cum %>% 
  ggplot(aes(
    peri_breaks,
    cum_licks,
    color = experiment_id,
    ymin = cum_licks - cum_err,
    ymax = cum_licks + cum_err
  )) +
  geom_line() +
  geom_point() +
  geom_errorbar(aes(fill = experiment_id)) +
  geom_vline(xintercept = 10.5)
```

### licks over time bins
```{r}
pr_bin_data_ind %>% 
  ggplot(aes(
    bins,
    m_licks,
    color = protocol,
    ymin = m_licks - err,
    ymax = m_licks + err
  )) +
  geom_line() +
  geom_point() +
  geom_errorbar() +
  facet_grid(experiment_id~n_sesion, scales = "free_y")
```

# statistical analysis

```{r}
# raw plot
pr_bin_data %>% 
  ggplot(aes(
    bins,
    mean_licks,
    ymin = mean_licks - err,
    ymax = mean_licks + err,
    color = experiment_id
  )) +
  geom_line() +
  geom_point() +
  geom_errorbar()

# statistical model 1
data_1 <- pr_bin_data_session
data_2 <- pr_bin_data_session_last_pool

# considering both controls as one control group
model_1 <- lmer(
  data = data_1,
  n_licks ~ experiment_id + (1 | ID)
)
summary(model_1)

# statistical model 2
model_2 <- lmer(
  data = data_1,
  n_licks ~ experiment_id * as.numeric(n_sesion) + (1 | ID)
)
summary(model_2)

# statistical model 3
model_3 <- lmer(
  data = data_1,
  n_licks ~ experiment_id * as.numeric(n_sesion) * bins + (1 | ID)
)
summary(model_3)

# considering only the last pool "high uncertainty"
model_4 <- lmer(
  data = data_2,
  n_licks ~ experiment_id + (1 | ID)
)
summary(model_4)

# statistical model 2
model_5 <- lmer(
  data = data_2,
  n_licks ~ experiment_id * as.numeric(n_sesion) + (1 | ID)
)
summary(model_5)

# statistical model 3
model_6 <- lmer(
  data = data_2,
  n_licks ~ experiment_id * as.numeric(n_sesion) * bins + (1 | ID)
)
summary(model_6)

# considering error by pool
model_7 <- lmer(
  data = data_1,
  n_licks ~ experiment_id + (1 | ID:pool)
)
summary(model_7)

# statistical model 2
model_8 <- lmer(
  data = data_1,
  n_licks ~ experiment_id * as.numeric(n_sesion) + (1 | ID:pool)
)
summary(model_8)

# statistical model 3
model_9 <- lmer(
  data = data_1,
  n_licks ~ experiment_id * as.numeric(n_sesion) * bins + (1 | ID:pool)
)
summary(model_9)
```

